Stateful Forward Reasoning

### 2025-02-11 paper.tex
rephrase

Given a set of propositions $\mathcal{P} := \{P_{i,j} | 1 \leq i \leq n \text{ and } 1 \leq j \leq 6\}$ and $\mathcal{Q} :=\{Q_{i} | 1 \leq i \leq n \}$, in this test, we consider the $n$ following rules $r_i : P_{i,1}\to \dots P_{i,6} \to Q_i$.
The procedures are then run on a context containing exactly $\mathcal{P}$.

In this case, we sketch the behavior of the stateless algorithm:
It pick a first hypothesis, $h_{i,j} : P_{i,j}$.
If $j < 6$, the index returns nothing and it selects another hypothesis.
For $h_{i,6} : P_{i,6}$, the rule $r_i$ is selected and it then needs to try and fill its remaining five slot with the context's $6n$ hypotheses which it tries all.
This gives a complexity of about $O(n^2)$.

>>>>

Given a set of propositions $\mathcal{P} := \{P_{i,j} | 1 \leq i \leq n \text{ and } 1 \leq j \leq 6\}$ and $\mathcal{Q} :=\{Q_{i} | 1 \leq i \leq n \}$, in this test, we consider the $n$ following rules $r_i : P_{i,1}\to \dots P_{i,6} \to Q_i$.
The procedures are then run on a context containing exactly $\mathcal{P}$.
In this case, we sketch the behavior of the stateless algorithm:
It pick a first hypothesis, $h_{i,j} : P_{i,j}$.
If $j < 6$, the index returns nothing and it selects another hypothesis.
For $h_{i,6} : P_{i,6}$, the rule $r_i$ is selected, and it then needs to try and fill its remaining five slot with the context's $6n$ hypotheses which it tries all.
This gives a complexity of about $O(n^2)$.
